%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jasper Geer} % Your name
\address{
  \href{mailto:jasper.geer@ubc.ca}{\textbf{jasper.geer@ubc.ca}}
  \\
  \href{https://www.jaspergeer.com}{\textbf{www.jaspergeer.com}}}
\usepackage{enumitem}
\setlist[itemize]{noitemsep}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf University of British Columbia} \hfill {\em 2024-Present}
\\ {\it Vancouver, British Columbia, Canada}
\\ Computer Science, PhD
\\ Supervised by Prof. Alexander J. Summers

\begin{itemize}
    \item Research in Programming Languages and Formal Verification in the UBC Software Practices Lab.
    \item Primarily interested in Rust verification, separation logic, and type systems.
    \item Contributor to Prusti, a Rust verifier developed in collaboration with ETH Zurich.
\end{itemize}

%--copy and paste this region  if you need more--
{\bf Tufts University} \hfill {\em 2020-2024}
\\ {\it Medford, Massachussets, USA}
\\ Computer Science, BS
\\ \textit{summa cum laude}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experiences}
%--copy and paste this region  if you need more--
{\bf Verifying Safe Clients of Interior Mutability} \hfill {\em August 2025 - Present}\\
with Alexander J. Summers\\
{\it University of British Columbia}
\begin{itemize}
    \item Developing formal underpinnings in separation logic for a verification methodology for safe clients of interior-mutable modules in Rust.
    \item Exploring extensions to the specification language and proof technique to support a wider range of use cases.
\end{itemize}

{\bf Place Capability Graphs} \hfill {\em January 2025 - 2025}\\
with Alexander J. Summers\\
{\it University of British Columbia}
\begin{itemize}
  \item Developed a MIR-level mutation testing tool for the Rust compiler to evaluate the trustworthiness of Place Capabilitiy Graphs, a model of Rust's type checking results.
  \item Co-author on paper published in OOPSLA 2025.
\end{itemize}

{\bf Type- and Name-Guided Program Synthesis} \hfill {\em September 2023 - September 2025}\\
with Jeffrey Foster \\
{\it Tufts University}
\begin{itemize}
    \item Implemented and formalized a subtyping constraint-guided program synthesis technique for Java programs.
    \item Developed search heuristics to make a larger class of synthesis problems tractable.
\end{itemize}

{\bf Technical Limitations and Novel Use Cases for Symbolic Execution} \hfill {\em September 2023 - May 2024}\\
with Daniel Votipka\\
{\it Tufts University}

\begin{itemize}
    \item Participated in an extensive review of recent symbolic execution and automated testing literature.
    \item Qualitatively coded rounds of 5-10 research papers and contributed to codebook development.
\end{itemize}
%--copy and paste this region  if you need more--
\end{rSection}

\newpage

\begin{rSection}{Professional Experiences}
{\bf Vehicle Software Intern} \hfill {\em May 2023 - August 2023}\\
\hfill {\it Tesla}
\begin{itemize}
    \item End-to-end feature development in Haskell for an incremental compiler frontend.
    \item Refactored compiler passes into incremental build rules for a monadic build system.
    \item Created embedded domain-specific languages to implement new language server features.
    \item Received offer for full-time conversion.
\end{itemize}
\end{rSection}

\begin{rSection}{Teaching}
{\bf University of British Columbia, Graduate Teaching Assistant} \hfill {\em September 2024 - Present}
\begin{itemize}
    \item CPSC411, Compilers. {\it Spring 2024.}
    \item CPSC311, Definition of Programming Languages. {\it Fall 2024.}
\end{itemize}

{\bf Tufts University, Teaching Fellow} \hfill {\em January 2024 - May 2024}
\begin{itemize}
    \item CS170, Computation Theory. {\it Spring 2024.}
\end{itemize}

{\bf Tufts University, Course Assistant} \hfill {\em September 2022 - December 2023}
\begin{itemize}
    \item CS170, Computation Theory. {\it Fall 2022, Spring 2023, Fall 2023.}
\end{itemize}

{\bf Coding With Kids} \hfill {\em May 2022 - September 2022}
\begin{itemize}
    \item Taught week-long programming classes for primary and secondary school students.
\end{itemize}
    
\end{rSection}

%--------------------------------------------------------------------------------
%    PUBLICATIONS -----------------------------------------------------------------------------------------------
\begin{rSection}{Publications} 
  Zachary Grannan, Aurel Bílý, Jonáš Fiala, \textbf{Jasper Geer}, Markus de Medeiros, Peter Müller, and Alexander J. Summers. 2025. \emph{Place Capability Graphs: A General-Purpose Model of Rust’s Ownership and Borrowing Guarantees}. Proc. ACM Program. Lang. 9, OOPSLA2, Article 344 (October 2025), 28 pages. https://doi.org/10.1145/3763122
\end{rSection}

%--------------------------------------------------------------------------------
%    AWARDS
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Awards} 
{\bf Four Year Doctoral Fellowship (4YF)}{, University of British Columbia
} \hfill{\em Jan 2026 - Dec 2029}

\end{rSection}

%--------------------------------------------------------------------------------
%    SERVICE
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Service} 
{\bf Reviewer}{, UBC Computer Science Student Research Conference}\hfill{\em January 2026}\\
{\bf VP Social}{, UBC Computer Science Graduate Student Association}\hfill{\em May 2025 - April 2026}\\
{\bf Tuesday Tea Organizer}{, UBC Computer Science Graduate Student Association}\hfill{\em May 2025 - April 2026}\\
{\bf PL Reading Group Organizer}{, UBC Software Practices Lab}\hfill{\em September 2024 - Present}

\end{rSection}

% %--------------------------------------------------------------------------------
% %    PROJECTS
% %-----------------------------------------------------------------------------------------------
% \begin{rSection}{Projects}
% %--copy and paste this region  if you need more--
% {\bf miniVerifier}
% \begin{itemize}
%     \item Symbolic-execution based verifier for a small programming language with Hoare-logic specifications.
%     \item Written in Haskell and produces SMT-LIBv2 scripts.
% \end{itemize}
% {\bf Compost}
% \begin{itemize}
%     \item LLVM frontend for a statically-typed functional programming language.
%     \item Designed an affine type system to enforce memory safety without runtime garbage collection.
%     \item Began as a personal summer project, completed as a semester-long group project in a compilers class.
%     \item Written in OCaml.
% \end{itemize}
% % {\bf Odin (Contributor)}\\
% % - Contributed to an open source compiler for the Odin programming language \\
% % - Addressed issues in the type checker and code generator \\
% {\bf tinyValidator}
% \begin{itemize}
%     \item Translation validator for a C-subset language by means of symbolic execution.
%     \item Devised a big-step operational semantics to describe the execution of programs with symbolic inputs.
%     \item Written in Haskell and uses the Z3 SMT solver.
% \end{itemize}
% % {\bf jumcc} \\
% % - Compiler from C subset targeting small virtual assembly language \\
% % - Pointers, arrays, functions, structured control flow, and header files \\
% % - Written in Haskell
% %--copy and paste this region  if you need more--
% \end{rSection}
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Programming Background}
Recent experience with Rust and Scala.\\
Previous experience with OCaml, Standard ML, Haskell, Racket, C, and Java.
\end{itemize}
\end{rSection}

\end{document}----------------------------

